Income Has Serious Implications On Many Facets of American Life in 2021

### 2022-03-21 outputs/paper/paper.Rmd
fifth commit

## Key features

@@

# Results

```{r}
#creating levels for the x and y axis on the graphs

@@

```{r fig1, fig.cap="write a figure caption here", echo = FALSE, fig.width=12, fig.height=10, echo=FALSE}
#income16 vs income grouped by gender

@@

income16_gender/income_gender
```

```{r, fig.cap="write a figure caption here", echo = FALSE, fig.width=12, fig.height=10, echo=FALSE}
#fincome16 vs income grouped by where grandparents were born

@@

```{r, fig.cap="write a figure caption here", echo = FALSE, fig.width=12, fig.height=10, echo=FALSE}
#family income at 16 grouped by where individual was born

@@

```{r, fig.cap="write a figure caption here", echo = FALSE, fig.width=9, fig.height=6, echo=FALSE}
#income at 16 vs current income grouped by where individual was born

>>>>

## Key features & Pros And Cons of the Methodology and Survey

@@

# Visualizing the Data and The Implications
In this analysis, I am interested at looking at how real is the American Dream and if it is found to be possible, whether or not there is any difference in attainment amoung genders. As such, in this Section \@ref(visualizingthedataandtheimplications), we will create various visuals which will enable us to extract as much information as we can and we will speak about the implications that they make.
```{r, echo = F, message = F, include = F}
#creating levels for the x and y axis on the graphs

@@

## Visual 1
```{r figure-1, fig.cap="write a figure caption here", echo = FALSE, fig.width=12, fig.height=10, message = F, warning = F}
income16_gender <- ggplot(mapping = aes(x = factor(income16_cat, level = level_income16), group = sex, fill = sex), data = reduced_data) +
  geom_bar(alpha = 0.7)  +
  theme_minimal() +
  labs(x = "Family Income at 16 Years Old",
       y = "Number of occurrences",
       fill = "Gender",
       title = "Total Family Income at 16 Grouped by Gender") +
  coord_flip()
income16_gender
```
In this graph (Figure \@ref(fig:figure-1)), we can proportions of family income when the responded was 16 years of age. We also see that an over-whelming majority of people in our sample had an income of over $40,000. We also see that the single largest individual group is the *NA* group. We will discuss the implications of this in Section \@ref(limitations1). As we've previously discussed, when the questioned is prompted with a question, in every situation, they have the option to refuse to answer the question or say that they do not know. The both of these are listed as NA responses. We also see that of the 5 possible genders (including the NA gender, not to be confused with the NA response to income16), the overwhelming majority of respondents identified as male or female as expected.

We would like to contrast this with the current income of responds. The below is the same graph above but we've also included a similar graph but for family income at the time of response 
```{r figure-2, fig.cap="write a figure caption here", echo = FALSE, fig.width=12, fig.height=10, message = F, warning = F}
#income16 vs income grouped by gender

@@

income16_gender/income_gender
```
In figure \@ref(fig:figure-2), we see the overlapping of the two graphs, the first of which is the same as figure \@ref(fig:fig1) and the bottom one is the same in essence but with the information for current family income instead of at age 16. The first and most striking part of this visual is that for the current income, the highest thres

```{r, fig.cap="write a figure caption here", echo = FALSE, fig.width=12, fig.height=10, message = F, warning = F}
#fincome16 vs income grouped by where grandparents were born

@@

```{r, fig.cap="write a figure caption here", echo = FALSE, fig.width=12, fig.height=10, message = F, warning = F}
#family income at 16 grouped by where individual was born

@@

```{r, fig.cap="write a figure caption here", echo = FALSE, fig.width=9, fig.height=6, message = F, warning = F}
#income at 16 vs current income grouped by where individual was born
